Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
Wording

Evidence for users should be documented with Haddock markup syntax.
For this purpose, we propose the followings:

\begin{itemize}
\item Define new Haddock markup for examples.
\item Define new Haddock markup for properties.
\item Bring Doctest from the Python community to the Haskell
community and integrate it with QuickCheck.
Examples and properties in Haddock comments is automatically
tested by the Doctest command.
Its implementation will be discussed in Section~\ref{sec:doctest}.

>>>>

Evidence that is useful as user documentation, should be included in
Haddock comments.  For this purpose, we propose the following:

\begin{itemize}
\item Add markup syntax for interactive examples to Haddock
\item Add markup syntax for properties to Haddock
\item Bring Doctest from the Python community to the Haskell
community and integrate it with QuickCheck.
Examples and properties in Haddock comments is automatically
tested by the Doctest command.
Its implementation will be discussed in Section~\ref{sec:doctest}.
